Copy number inference with InferCNV

### 2024-05-15 analyses/cell-type-ewings/04-infercnv.Rmd
update notebook to read in cnv metadata

# The path to this module
module_base <- file.path(repository_base, "analyses", "ewings-cell-type")
```

@@

all_results_dir_list <- c(
  no_ref = file.path(results_dir, "no_reference"),
  with_ref = file.path(results_dir, "endothelial_reference")
)
```

@@

@@

The predictions information lies in a few files that live in the output directory. 
We want to know which cells had CNVs and how many CNVs were found. 
To map the information about CNVs to individual cells, they recommend using the `infercnv::add_to_seurat()` function which takes the output directory from running `InferCNV` and reads in all necessary files and adds the per cell CNV information to the `meta.data`. 
So we will start by converting our processed SCE object to a Seurat object, incorporate the CNV information, and then add the CNV information to the SCE object.

```{r}
infer_cnv_dir <- all_results_dir_list["with_ref"]

# first create a Seurat object from our SCE object
seurat_obj <- scpcaTools::sce_to_seurat(sce)

# add in the CNV information 
# this adds new columns to the meta.data indicating presence of CNVs for each chromosome
seurat_obj <- infercnv::add_to_seurat(seurat_obj = seurat_obj,
                                      infercnv_output_path = infer_cnv_dir)

# grab metadata from Seurat and add back to SCE 
seurat_metadata <- seurat_obj@meta.data |> 
  dplyr::select(-c(orig.ident, nCount_RNA, nFeature_RNA))

colData(sce) <- DataFrame(seurat_metadata, row.names = seurat_metadata$barcodes)
```

@@

```{r}
# make df for plotting
coldata_df <- sce |> 
  scuttle::makePerCellDF(use.dimred = "UMAP") |> 
  # replace UMAP.1 with UMAP1
  dplyr::rename_with(
        \(x) stringr::str_replace(x, "^UMAP\\.", "UMAP")
      )

>>>>

# The path to this module
module_base <- file.path(repository_base, "analyses", "cell-type-ewings")
```

@@

all_results_dir_list <- c(
  no_ref = file.path(results_dir, "no_reference"),
  with_ref = file.path(results_dir, "endothelial_reference")
)

# with ref cnv metadata file 
cnv_metadata_file <- file.path(results_dir, "endothelial_reference", glue::glue("{params$library_id}_cnv-metadata.tsv"))
```

@@

# read in cnv metadata 
cnv_metadata_df <- readr::read_tsv(cnv_metadata_file)

@@

Before we can make any plots we need to add some metadata that contains CNV information on a per cell level to the cell metadata.

```{r}
# make df for plotting
coldata_df <- sce |> 
  scuttle::makePerCellDF(use.dimred = "UMAP") |> 
  # replace UMAP.1 with UMAP1
  dplyr::rename_with(
        \(x) stringr::str_replace(x, "^UMAP\\.", "UMAP")
      ) |> 
  # add in per cell cnv information 
  dplyr::left_join(cnv_metadata_df, by = c("barcodes"))

@@
